Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-02 WSSSPE3/report/registrants.tex
Replied to Dan's note.

Alice Allen & Astrophysics Source Code Library\\
Gabrielle Allen & NCSA\\
Janine Aquino & UCAR/NCAR Earth Observing Laboratory\\
Steven Brandt & Louisiana State University\\
Jed Brown & CU Boulder\\
Matthias Bussonnier & UC Berkeley\\
Jeffrey Carver & University of Alabama\\
Emily Chen & NCSA\\
Sou Cheng Choi & NORC at UChicago / IIT\\
Nancy Collins & NCAR\\
Ethan Davis & UCAR Unidata\\
Davide DelVento & NCAR/CISL\\
Yuhan Ding & Illinois Institute of Technology\\
Tim Dunne & KnowInnovation \\
Ward Fisher & UCAR/Unidata\\
Sandra Gesing & University of Notre Dame\\
Josh Greenberg & Sloan Foundation\\
Dan Gunter & LBNL\\
Ted Habermann & The HDF Group\\
James Hetherington & University College London\\
Neil Chue Hong & Software Sustainability Institute\\
Elisabeth Huffer & Lingua Logica/NASA \\
Lorraine Hwang & UC Davis - CIG\\
Raymond Idaszak & RENCI; University of North Carolina at Chapel Hill\\
Elizabeth Jessup & University of Colorado Boulder\\
Nick Jones & New Zealand eScience Infrastructure (NeSI)\\
Daniel Katz & U Chicago & Argonne\\
Iain Larmour & EPSRC (UK)\\
Frank Löffler & Louisiana State University\\
Suresh Marru & Indiana University\\
Ryan May & UCAR/Unidata\\
Abigail Cabunoc Mayes & Mozilla Foundation\\
Jeff McWhirter & Geode Systems\\
Constantinos Michailidis & Knowinnovation\\
Don Middleton & NCAR\\
Mark Miller & SDSC\\
Pate Motter & University of Colorado\\
Jaroslaw Nabrzyski & University of Notre Dame\\
Patrick Nichols & National Center for Atmospheric Research\\
Kyle Niemeyer & Oregon State University\\
Laura Owen & NCSA\\
Abani Patra & Univ at Buffalo\\
Grace Peng & National Center for Atmospheric Research\\
Birgit Penzenstadler & California State University Long Beach\\
Lindsay Powers & The HDF Group\\
Bernie Randles & UCLA\\
Erin Robinson & Foundation for Earth Science\\
Daniel Sellars & CANARIE Inc\\
Nikolay Simakov & SUNY University at Buffalo\\
Ian Taylor & Cardiff University\\
Ilian Todorov & Science & Technology Facilities Council, UK\\
Benjamin Tovar & University of Notre Dame\\
Gregory Tucker & University of Colorado at Boulder\\
Matthew Turk & NCSA\\
Colin Venters & University of Huddersfield\\
Alexander Vyushkov & University of Notre Dame\\
Fraser Watson & National Solar Observatory\\
Nic Weber & University of Washington\\
Daniel Ziskin & NCAR - ACOM\\

>>>>

Alice Allen & \href{mailto:aallen@ascl.net}{aallen@ascl.net}&Astrophysics Source Code Library\\
Gabrielle Allen & \href{mailto:gdallen@illinois.edu}{gdallen@illinois.edu}&NCSA\\
Janine Aquino & \href{mailto:janine@ucar.edu}{janine@ucar.edu}&UCAR/NCAR Earth Observing Laboratory\\
Steven Brandt & \href{mailto:sbrandt@cct.lsu.edu}{sbrandt@cct.lsu.edu}&Louisiana State University\\
Jed Brown & \href{mailto:jed@jedbrown.org}{jed@jedbrown.org}&CU Boulder\\
Matthias Bussonnier & \href{mailto:bussonniermatthias@gmail.com}{bussonniermatthias@gmail.com}&UC Berkeley\\
Jeffrey Carver & \href{mailto:carver@cs.ua.edu}{carver@cs.ua.edu}&University of Alabama\\
Emily Chen & \href{mailto:echen35@illinois.edu}{echen35@illinois.edu}&NCSA\\
Sou Cheng Choi & \href{mailto:sctchoi@uchicago.edu}{sctchoi@uchicago.edu}&NORC at UChicago / IIT\\
Nancy Collins & \href{mailto:nancy@ucar.edu}{nancy@ucar.edu}&NCAR\\
Ethan Davis & \href{mailto:edavis@ucar.edu}{edavis@ucar.edu}&UCAR Unidata\\
Davide DelVento & \href{mailto:ddvento@ucar.edu}{ddvento@ucar.edu}&NCAR/CISL\\
Yuhan Ding & \href{mailto:yding2@hawk.iit.edu}{yding2@hawk.iit.edu}&Illinois Institute of Technology\\
Tim Dunne & \href{mailto:tim.dunne@knowinnovation.com}{tim.dunne@knowinnovation.com}&KnowInnovation \\
Ward Fisher & \href{mailto:wfisher@ucar.edu}{wfisher@ucar.edu}&UCAR/Unidata\\
Sandra Gesing & \href{mailto:sandra.gesing@nd.edu}{sandra.gesing@nd.edu}&University of Notre Dame\\
Josh Greenberg & \href{mailto:greenberg@sloan.org}{greenberg@sloan.org}&Sloan Foundation\\
Dan Gunter & \href{mailto:dkgunter@lbl.gov}{dkgunter@lbl.gov}&LBNL\\
Ted Habermann & \href{mailto:thabermann@hdfgroup.org}{thabermann@hdfgroup.org}&The HDF Group\\
James Hetherington & \href{mailto:jamespjh@gmail.com}{jamespjh@gmail.com}&University College London\\
Neil Chue Hong & \href{mailto:N.ChueHong@software.ac.uk}{N.ChueHong@software.ac.uk}&Software Sustainability Institute\\
Elisabeth Huffer & \href{mailto:beth@lingualogica.net}{beth@lingualogica.net}&Lingua Logica/NASA \\
Lorraine Hwang & \href{mailto:ljhwang@ucdavis.edu}{ljhwang@ucdavis.edu}&UC Davis - CIG\\
Raymond Idaszak & \href{mailto:rayi@renci.org}{rayi@renci.org}&RENCI; University of North Carolina at Chapel Hill\\
Elizabeth Jessup & \href{mailto:jessup@cs.colorado.edu}{jessup@cs.colorado.edu}&University of Colorado Boulder\\
Nick Jones & \href{mailto:nick.jones@nesi.org.nz}{nick.jones@nesi.org.nz}&New Zealand eScience Infrastructure (NeSI)\\
Daniel Katz & \href{mailto:dsk@uchicago.edu}{dsk@uchicago.edu}&U Chicago \& Argonne\\
Iain Larmour & \href{mailto:Iain.Larmour@epsrc.ac.uk}{Iain.Larmour@epsrc.ac.uk}&EPSRC (UK)\\
Frank Löffler & \href{mailto:knarf@cct.lsu.edu}{knarf@cct.lsu.edu}&Louisiana State University\\
Suresh Marru & \href{mailto:smarru@iu.edu}{smarru@iu.edu}&Indiana University\\
Ryan May & \href{mailto:rmay@ucar.edu}{rmay@ucar.edu}&UCAR/Unidata\\
Abigail Cabunoc Mayes & \href{mailto:abigail@mozillafoundation.org}{abigail@mozillafoundation.org}&Mozilla Foundation\\
Jeff McWhirter & \href{mailto:jeff.mcwhirter@gmail.com}{jeff.mcwhirter@gmail.com}&Geode Systems\\
Constantinos Michailidis & \href{mailto:costa.michailidis@knowinnovation.com}{costa.michailidis@knowinnovation.com}&Knowinnovation\\
Don Middleton & \href{mailto:don@ucar.edu}{don@ucar.edu}&NCAR\\
Mark Miller & \href{mailto:mark.alan.miller2@gmail.com}{mark.alan.miller2@gmail.com}&SDSC\\
Pate Motter & \href{mailto:pate.motter@colorado.edu}{pate.motter@colorado.edu}&University of Colorado\\
Jaroslaw Nabrzyski & \href{mailto:naber@nd.edu}{naber@nd.edu}&University of Notre Dame\\
Patrick Nichols & \href{mailto:pnichols@ucar.edu}{pnichols@ucar.edu}&National Center for Atmospheric Research\\
Kyle Niemeyer & \href{mailto:Kyle.Niemeyer@oregonstate.edu}{Kyle.Niemeyer@oregonstate.edu}&Oregon State University\\
Laura Owen & \href{mailto:lowen@illinois.edu}{lowen@illinois.edu}&NCSA\\
Abani Patra & \href{mailto:abani@buffalo.edu}{abani@buffalo.edu}&Univ at Buffalo\\
Grace Peng & \href{mailto:grace@ucar.edu}{grace@ucar.edu}&National Center for Atmospheric Research\\
Birgit Penzenstadler & \href{mailto:Birgit.Penzenstadler@csulb.edu}{Birgit.Penzenstadler@csulb.edu}&California State University Long Beach\\
Lindsay Powers & \href{mailto:lpowers@hdfgroup.org}{lpowers@hdfgroup.org}&The HDF Group\\
Bernie Randles & \href{mailto:randles@ucla.edu}{randles@ucla.edu}&UCLA\\
Erin Robinson & \href{mailto:erinrobinson@esipfed.org}{erinrobinson@esipfed.org}&Foundation for Earth Science\\
Daniel Sellars & \href{mailto:dan.sellars@canarie.ca}{dan.sellars@canarie.ca}&CANARIE Inc\\
Nikolay Simakov & \href{mailto:nikolays@buffalo.edu}{nikolays@buffalo.edu}&SUNY University at Buffalo\\
Ian Taylor & \href{mailto:ian.j.taylor@gmail.com}{ian.j.taylor@gmail.com}&Cardiff University\\
Ilian Todorov & \href{mailto:ilian.todorov@stfc.ac.uk}{ilian.todorov@stfc.ac.uk}&Science \& Technology Facilities Council, UK\\
Benjamin Tovar & \href{mailto:btovar@nd.edu}{btovar@nd.edu}&University of Notre Dame\\
Gregory Tucker & \href{mailto:gtucker@colorado.edu}{gtucker@colorado.edu}&University of Colorado at Boulder\\
Matthew Turk & \href{mailto:mjturk@illinois.edu}{mjturk@illinois.edu}&NCSA\\
Colin Venters & \href{mailto:colin.venters@googlemail.com}{colin.venters@googlemail.com}&University of Huddersfield\\
Alexander Vyushkov & \href{mailto:avyushko@nd.edu}{avyushko@nd.edu}&University of Notre Dame\\
Fraser Watson & \href{mailto:fwatson@nso.edu}{fwatson@nso.edu}&National Solar Observatory\\
Nic Weber & \href{mailto:nmweber@uw.edu}{nmweber@uw.edu}&University of Washington\\
Daniel Ziskin & \href{mailto:ziskin@ucar.edu}{ziskin@ucar.edu}&NCAR - ACOM\\
